Estimating Daily Bicycle Counts in Seattle from Seasonal and Weather Factors

### 2014-12-08 article/article.tex
make hypotheses more explicit in the introduction

This article contributes to that understanding by focusing on the
substantive effects of weather and seasonality on the number of
bicyclists observed on a given day. In order to address these two
primary research questions, we develop a statistical model estimated
using two years of automated bicycle counts collected on Seattle's
Fremont Street bridge, as well as historic weather and season data
collected from other sources.

>>>>

This article contributes to that understanding by focusing on the
substantive effects of weather and seasonality on the number of
bicyclists observed on a given day. Specifically, we hypothesize that
factors associated with inclement weather (low temperature and
precipitation) will be inversely correlated with bicycle counts. We
similarly expect to see an additional decrease in counts associated
with physical and social / institutional aspects of season. That is, in seasons
where the days get shorter, we expect fewer cyclists due to a kind of
decision making inertia. We also expect fewer cyclists outside
the ``school season.''

In order to address these two
primary research questions, we develop a statistical model estimated
using two years of automated bicycle counts collected on Seattle's
Fremont Street bridge, as well as historic weather and season data
collected from other sources.
